

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readr)

```



```{r}
print('TESTING')
```


## Motivation

The motivation of the project is to understand the different perspectives of these three different projects (CCLE, genomics of drug sensitivity in cancer, Cancer Therapeutics Response Portal) working on cell lines, as they measure different variables or components that are read from the cell line patients.

Project Summaries
Cancer Cell Line Encyclopedia (CCLE)
The Cancer Cell Line Encyclopedia (CCLE) project aims to characterize the genetic and pharmacologic profiles of a large panel of human cancer cell lines to develop predictive models for cancer drug sensitivity. It provides a comprehensive dataset, including gene expression, copy number, and mutation data, for over 1,000 cancer cell lines.


<br>

## CSV files

Lets review the observed files from the Depmap portal

#### sampple_info19Q3.csv  
sample_info.csv: This file contains metadata about cell lines in the CCLE project. It includes information such as cell line names, aliases, COSMIC IDs, sex, source, sample collection site, primary disease, subtype, age, Sanger Model ID, lineage, and various other details. Each row represents a unique cell line, and the primary key is depmap_id (Cancer cell line primary key).
<br>

